---
title: ""
author: "Seb Dalgarno"
date: '2018-10-14'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r work-experience-data, include=FALSE, echo=FALSE}
library(ggplot2)
library(plotly)
library(tibble)
library(dplyr)
library(lubridate)

pc.desc <- "Statistical modeling (Maximum Likelihood, Bayesian); R package development/maintenance; SQLite database creation/management; Shiny app development; spatial data management/manipulation in R; data visualization/map creation in R."

se.desc <- "Various tasks in R: statistical modelling; GIS and spatial analysis; data cleaning and SQLite database creation/management; data visualization; report creation. Contracts with Parks Canada, Habitat Conservation Trust Foundation, Ministry of Forests, Lands and Natural Resource Operations, and Gowgaia Institute."

rg.desc <- "Species Distribution Modelling; shorebird and coastal/intertidal ecology; designed and conducted field work in remote Gwaii Haanas National Park Reserve over 3 weeks by kayak; all analyses/ data management done in R; results published in Avian Conservation Ecology journal."

ta.desc <- "Prepared and delivered presentations; supervised labs; graded assignments; topics covered by courses included statistical analysis, GIS and spatial analysis, remote sensing."

cws.desc <- "Lived and worked in remote part of K'uuna Gwaay Heritage Site/Conservancy retrieving ankle- band GPS loggers from breeding seabirds."

wcs.desc <- "Designed several scientific studies and managed/conducted field work in remote parts of Papua New Guinean forest; conducted statistical analyses, GIS; results published in Pacific Conservation Biology journal."

uot.desc <- "Assisted Professor Neera Singh; conducted research on decentralized forest governance, community forestry, and carbon emission reduction projects from deforestation (REDD); prepared manuscripts for publication. "

df <- tibble(Employer = c("Poisson Consulting Ltd.",
                          "Self Employed",
                          "University of Guelph",
                          "University of Guelph",
                          "Canadian Wildlife Service",
                          "Wildlife Conservation Society",
                          "University of Toronto"),
             Role = c("Computational Biologist",
                      "Consultant",
                      "Researcher",
                      "Teaching Assistant",
                      "Researcher",
                      "Research Intern",
                      "Research Assistant"
                      ),
             Location = c("Haida Gwaii, BC",
                          "Haida Gwaii, BC",
                          "Guelph, ON",
                          "Guelph, ON",
                          "Haida Gwaii, BC",
                          "Manus, Papua New Guinea",
                          "Toronto, ON"
                          ),
             DateStart = c(ymd("2017-01-01"),
                           ymd("2016-09-01"),
                           ymd("2015-09-01"),
                           ymd("2014-09-01"),
                           ymd("2014-05-01"),
                           ymd("2012-09-01"),
                           ymd("2011-09-01")
                           ),
             DateEnd = c(Sys.Date(),
                         ymd("2016-12-31"),
                         ymd("2016-09-01"),
                         ymd("2016-09-01"),
                         ymd("2014-05-20"),
                         ymd("2014-09-01"),
                         ymd("2012-09-01")
                         ),
             Description = c(pc.desc,
                             se.desc,
                             rg.desc,
                             ta.desc,
                             cws.desc,
                             wcs.desc,
                             uot.desc
                             ))

msc.desc <- "Predictive modeling of Black Oystercatcher distribution in Haida Gwaii, BC "

dfe <- tibble(University = c("University or Toronto",
                             "University of Guelph"),
              Degree = c("B.A. Forest Conservation",
                         "M.Sc. Geography"
                         ),
              DateStart = c(ymd("2006-09-01"),
                            ymd("2014-09-01")),
              DateEnd = c(ymd("2011-05-01"),
                          ymd("2016-09-01")))
```
## Seb Dalgarno  
\

#### Masset, BC  
#### seb.dalgarno@gmail.com - 250-626-8978  

I am an ecologist with 4 years of R programming experience. My key skills include: R package development; Shiny web app development; statistical modelling; SQLite database creation/ querying; data visualization; spatial data management/manipulation (top user of [sf StackOverflow tag](https://stackoverflow.com/tags/sf/topusers)). I also have experience with JavaScript (leaflet.js, d3.js) HTML and CSS for web-based interactive data visualization. Finally, I have published work in scientific journals and have extensive experience managing and conducting remote ecological fieldwork.

* [GitHub](https://github.com/sebdalgarno)
* [StackOverflow](https://stackoverflow.com/users/7911031/sebdalgarno)  
\

### EDUCATION {.tabset .tabset-fade}
#### plot

```{r education-plot, echo=FALSE}

dfe %<>% arrange(DateStart) %>%
  mutate(row = as.character(1:nrow(dfe)))
gpe <- ggplot(data = dfe, aes(x = DateStart, xend = DateEnd, 
                            y = row, yend = row, color = row,
                            group = 1,
                    text = paste('University:', University, "<br>",
                                 'Degree:', Degree, "<br>",
                                 "Start Date:", as.character(DateStart), "<br>", 
                                 "End Date:", as.character(DateEnd)))) + 
  geom_segment(size = 6, show.legend = FALSE) + 
  labs(x = NULL, y = NULL) +
  theme_classic() +
  ggtitle("Hover over segment start/end to view more information.") +
  theme(axis.text = element_text(size = 10),
        axis.text.y = element_blank(),
        plot.title = element_text(size = 8)) 

ggplotly(gpe, tooltip = c("text"), height = 150) %>% hide_legend() %>% config(displayModeBar = F)
```

#### text
##### MSc, Geography
###### University of Guelph - Guelph, ON 
###### September 2014 to May 2016
* `r msc.desc` 
\  

##### BA, Forest Conservation
###### University of Toronto - Toronto, ON 
###### September 2006 to May 2011  
\  

#### table

```{r education-table, echo=FALSE}
library(DT)
datatable(dfe, class = "compact stripe", options = list(lengthChange = FALSE)) %>%
  DT::formatStyle(columns = c(1:6), fontSize = '85%')
```


</div>

### WORK EXPERIENCE {.tabset .tabset-fade}
#### plot

```{r work-experience-plot, echo=FALSE}
library(plotly)
library(RColorBrewer)

df %<>% arrange(DateStart) %>%
  mutate(row = as.character(1:nrow(df)))
gp <- ggplot(data = df, aes(x = DateStart, xend = DateEnd, 
                            y = row, yend = row, color = row,
                            group = 1,
                    text = paste('Role:', Role, "<br>",
                                 'Employer:', Employer, "<br>",
                                 'Location:', Location, "<br>",
                                 "Start Date:", as.character(DateStart), "<br>", 
                                 "End Date:", as.character(DateEnd)))) + 
  geom_segment(size = 6, show.legend = FALSE) + 
  labs(x = NULL, y = NULL) +
  theme_classic() +
  ggtitle("Hover over segment start/end to view more information.") +
  theme(axis.text = element_text(size = 10),
        axis.text.y = element_blank(),
        plot.title = element_text(size = 8)) 

ggplotly(gp, tooltip = c("text"), height = 300) %>% hide_legend() %>% config(displayModeBar = F)
```

#### text
##### Computational Biologist
###### Poisson Consulting Ltd. - Masset, BC  
###### January 2017 to Present  
* `r pc.desc`

##### Self-employed Consultant
###### Masset, BC  
###### September 2016 to January 2017  
* `r se.desc`

##### Researcher
###### University of Guelph - Guelph, ON
###### September 2015 to September 2016
* `r rg.desc`
\  

##### Teaching Assistant 
###### University of Guelph - Guelph, ON -
###### September 2014 to September 2016
* `r ta.desc` 
\  

##### Researcher
###### Canadian Wildlife Service - Queen Charlotte, BC
###### May 2014 to May 2014
* `r cws.desc`  
\  

##### Research Intern
###### Wildlife Conservation Society - Lorengau, Manus, Papua New Guinea
###### September 2012 to September 2014
* `r wcs.desc` 
\  

##### Research Assistant
###### University of Toronto - Toronto, ON
###### September 2011 to September 2012
* `r uot.desc` 
\  

#### table

```{r work-experience-table, echo=FALSE}
library(DT)
datatable(df, class = "compact stripe", options = list(lengthChange = FALSE)) %>%
  DT::formatStyle(columns = c(1:6), fontSize = '85%')
```

### PUBLISHED WORK
##### Scientific Papers
* Dalgarno, S., J. E. Mersey, Z. Gedalof, and M. Lemon. 2017. Species-environment associations and predicted distribution of Black Oystercatcher breeding pairs in Haida Gwaii, British Columbia, Canada. Avian Conservation and Ecology 12(2):9. 
[link to paper](http://www.ace-eco.org/vol12/iss2/art9/)
* Arihafa, A., Dalgarno, S., and E. Neale. 2017.An estimate of above-ground carbon stock in tropical rainforest on Manus Island, Papua New Guinea. Pacific Conservation Biology 21(4) 307-314.
[link to paper](http://www.publish.csiro.au/PC/PC15015)

##### Selected Technical Reports
* [Quesnel Lake Exploitation Analysis](https://www.poissonconsulting.ca/analyses/2018/04/11/quesnel-exploit-17.html)
* [Kaslo Bull Trout Productivity](https://www.poissonconsulting.ca/analyses/2018/04/17/kaslo-bt-recruits-17.html)

##### Selected R packages
* [dbflobr](https://github.com/poissonconsulting/dbflobr)
* [haidawave](https://github.com/sebdalgarno/haidawave)

##### Selected (public) Shiny apps
* [Yield per Recruit tool](https://poissonconsulting.shinyapps.io/ypr-shiny/)
* [Kootenay Lake Trout Movement app](https://poissonconsulting.shinyapps.io/klexdatr-movement/)  
\  

### SKILLS
`d3.js`, `leaflet.js`, `HTML`, `CSS`, `QGIS`, `ArcGIS`, `SQLite`, `Shiny`, `Machine Learning`, `Generalized Linear Model`, `R`, `Git`, `GitHub`, `Rstudio`, `ggplot2`, `tidyverse`  
\  

### CERTIFICATIONS/LICENCES
* PADI Open Water Diver  
* Swiftwater Safety Rescue Technician Level 3  
* Occupational First Aid


