---
title: ""
author: "Seb Dalgarno"
date: '2018-10-14'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r work-experience-data, include=FALSE, echo=FALSE}
library(ggplot2)
library(plotly)
library(tibble)
library(dplyr)
library(lubridate)

pc.desc <- "Statistical modeling (Maximum Likelihood, Bayesian); R package development/maintenance; SQLite database creation/management; Shiny app development; spatial data management/manipulation in R; data visualization/map creation in R."

se.desc <- "Various tasks in R: statistical modelling; GIS and spatial analysis; data cleaning and SQLite database creation/management; data visualization; report creation. Contracts with Parks Canada, Habitat Conservation Trust Foundation, Ministry of Forests, Lands and Natural Resource Operations, and Gowgaia Institute."

rg.desc <- "Species Distribution Modelling; shorebird and coastal/intertidal ecology; designed and conducted field work in remote Gwaii Haanas National Park Reserve over 3 weeks by kayak; all analyses/ data management done in R; results published in Avian Conservation Ecology journal."

ta.desc <- "Prepared and delivered presentations; supervised labs; graded assignments; topics covered by courses included statistical analysis, GIS and spatial analysis, remote sensing."

cws.desc <- "Lived and worked in remote part of K'uuna Gwaay Heritage Site/Conservancy retrieving ankle- band GPS loggers from breeding seabirds."

wcs.desc <- "Designed several scientific studies and managed/conducted field work in remote parts of Papua New Guinean forest; conducted statistical analyses, GIS; results published in Pacific Conservation Biology journal."

uot.desc <- "Assisted Professor Neera Singh; conducted research on decentralized forest governance, community forestry, and carbon emission reduction projects from deforestation (REDD); prepared manuscripts for publication. "

df <- tibble(Employer = c("Poisson Consulting Ltd.",
                          "Self Employed",
                          "University of Guelph",
                          "University of Guelph",
                          "Canadian Wildlife Service",
                          "Wildlife Conservation Society",
                          "University of Toronto"),
             Role = c("Computational Biologist",
                      "Consultant",
                      "Researcher",
                      "Teaching Assistant",
                      "Researcher",
                      "Research Intern",
                      "Research Assistant"
                      ),
             Location = c("Haida Gwaii, BC",
                          "Haida Gwaii, BC",
                          "Guelph, ON",
                          "Guelph, ON",
                          "Haida Gwaii, BC",
                          "Manus, Papua New Guinea",
                          "Toronto, ON"
                          ),
             DateStart = c(ymd("2017-01-01"),
                           ymd("2016-09-01"),
                           ymd("2015-09-01"),
                           ymd("2014-09-01"),
                           ymd("2014-05-01"),
                           ymd("2012-09-01"),
                           ymd("2011-09-01")
                           ),
             DateEnd = c(Sys.Date(),
                         ymd("2016-12-31"),
                         ymd("2016-09-01"),
                         ymd("2016-09-01"),
                         ymd("2014-06-01"),
                         ymd("2014-09-01"),
                         ymd("2012-09-01")
                         ),
             Description = c(pc.desc,
                             se.desc,
                             rg.desc,
                             ta.desc,
                             cws.desc,
                             wcs.desc,
                             uot.desc
                             ))

df <- df %>% mutate(`Start Date` = format(DateStart, "%B %d, %Y"),
                    `End Date` = if_else(Employer == "Poisson Consulting Ltd.", "Ongoing", format(DateEnd, "%B %d, %Y")))

msc.desc <- "Predictive modeling of Black Oystercatcher distribution in Haida Gwaii, BC"
ba.desc <- "Interdisciplinary coursework on forestry and forest conservation, including core science requirements."

dfe <- tibble(University = c("University or Toronto",
                             "University of Guelph"),
              Degree = c("B.A. Forest Conservation",
                         "M.Sc. Geography"
                         ),
              Location = c("Toronto, ON",
                           "Guelph, ON"),
              DateStart = c(ymd("2006-09-01"),
                            ymd("2014-09-01")),
              DateEnd = c(ymd("2011-05-01"),
                          ymd("2016-09-01")),
              Description = c(ba.desc, msc.desc))

dfe <- dfe %>% mutate(`Start Date` = format(DateStart, "%B %d, %Y"),
                    `End Date` = format(DateEnd, "%B %d, %Y"))
```
## Seb Dalgarno  
\

#### Tow Hill, Haida Gwaii, BC  -  seb.dalgarno@gmail.com  -  250-626-8978  
\

I am a computational biologist with 4 years of R programming experience. My key skills include: R package development; statistical modelling; Shiny app and web development; SQLite database management; SQL; data visualization; spatial data management/manipulation (top user of [sf StackOverflow tag](https://stackoverflow.com/tags/sf/topusers)). I have published work in scientific journals, co-authored numerous technical reports, and have experience managing and conducting remote ecological fieldwork.

* [GitHub](https://github.com/sebdalgarno)
* [StackOverflow](https://stackoverflow.com/users/7911031/sebdalgarno)  
\

### EDUCATION {.tabset .tabset-fade}
#### plot

```{r education-plot, echo=FALSE}

dfe %<>% arrange(DateStart) %>%
  mutate(row = as.character(1:nrow(dfe)))
gpe <- ggplot(data = dfe, aes(x = DateStart, xend = DateEnd, 
                            y = row, yend = row, color = row,
                            group = 1,
                    text = paste('University:', University, "<br>",
                                 'Degree:', Degree, "<br>",
                                 "Start Date:", `Start Date`, "<br>", 
                                 "End Date:", `End Date`))) + 
  geom_segment(size = 6, show.legend = FALSE) + 
  labs(x = NULL, y = NULL) +
  theme_classic() +
  ggtitle("Hover over segment start/end to view more information.") +
  theme(axis.text = element_text(size = 10),
        axis.text.y = element_blank(),
        plot.title = element_text(size = 8)) +
  scale_x_date(limits = c(min(dfe$DateStart), max(df$DateEnd)))

ggplotly(gpe, tooltip = c("text"), height = 150) %>% hide_legend() %>% config(displayModeBar = F)
```

#### text
```{r education-text, echo=FALSE, results = 'asis'}
dfe <- dfe %>% arrange(desc(DateStart))
for(i in 1:nrow(dfe)){
  cat("#####", dfe$Degree[i], "\n")
  cat("######", dfe$University[i], " - ", dfe$Location[i], "\n")
  cat("######", dfe$`Start Date`[i], "to", dfe$`End Date`[i], "\n\n")
  cat("*", dfe$Description[i], "\n\n")
}
```

<!-- #### table -->

<!-- ```{r education-table, echo=FALSE} -->
<!-- library(DT) -->
<!-- datatable(dfe %>% select(-row, -DateStart, -DateEnd), class = "compact stripe", options = list(lengthChange = FALSE)) %>% DT::formatStyle(columns = c(1:6), fontSize = '85%') -->
<!-- ``` -->


### WORK EXPERIENCE {.tabset .tabset-fade}
#### plot

```{r work-experience-plot, echo=FALSE}
library(plotly)
library(RColorBrewer)

df %<>% arrange(DateStart) %>%
  mutate(row = as.character(1:nrow(df)))
gp <- ggplot(data = df, aes(x = DateStart, xend = DateEnd, 
                            y = row, yend = row, color = row,
                            group = 1,
                    text = paste('Role:', Role, "<br>",
                                 'Employer:', Employer, "<br>",
                                 'Location:', Location, "<br>",
                                 "Start Date:", `Start Date`, "<br>", 
                                 "End Date:", `End Date`))) + 
  geom_segment(size = 6, show.legend = FALSE) + 
  labs(x = NULL, y = NULL) +
  theme_classic() +
  ggtitle("Hover over segment start/end to view more information.") +
  theme(axis.text = element_text(size = 10),
        axis.text.y = element_blank(),
        plot.title = element_text(size = 8)) +
  scale_x_date(limits = c(min(dfe$DateStart), max(df$DateEnd)))

ggplotly(gp, tooltip = c("text"), height = 300) %>% hide_legend() %>% config(displayModeBar = F)
```

#### text
```{r work-experience-text, echo=FALSE, results = 'asis'}
df <- df %>% arrange(desc(DateEnd))
for(i in 1:nrow(df)){
  cat("#####", df$Role[i], "\n")
  cat("######", df$Employer[i], " - ", df$Location[i], "\n")
  cat("######", df$`Start Date`[i], "to", df$`End Date`[i], "\n\n")
  cat("*", df$Description[i], "\n\n")
}
```

<!-- #### table -->

<!-- ```{r work-experience-table, echo=FALSE} -->
<!-- library(DT) -->
<!-- datatable(df %>% select(-row, -DateStart, -DateEnd), class = "compact stripe", options = list(lengthChange = FALSE)) %>% -->
<!--   DT::formatStyle(columns = c(1:6), fontSize = '85%') -->
<!-- ``` -->

### PUBLISHED WORK
##### Scientific Papers
* Dalgarno, S., J. E. Mersey, Z. Gedalof, and M. Lemon. 2017. Species-environment associations and predicted distribution of Black Oystercatcher breeding pairs in Haida Gwaii, British Columbia, Canada. Avian Conservation and Ecology 12(2):9. 
[link to paper](http://www.ace-eco.org/vol12/iss2/art9/)
* Arihafa, A., Dalgarno, S., and E. Neale. 2017.An estimate of above-ground carbon stock in tropical rainforest on Manus Island, Papua New Guinea. Pacific Conservation Biology 21(4) 307-314.
[link to paper](http://www.publish.csiro.au/PC/PC15015)

##### Selected Technical Reports
* [Quesnel Lake Exploitation Analysis](https://www.poissonconsulting.ca/analyses/2018/04/11/quesnel-exploit-17.html)
* [Kaslo Bull Trout Productivity](https://www.poissonconsulting.ca/analyses/2018/04/17/kaslo-bt-recruits-17.html)

##### Selected R packages
* [tinter](https://github.com/poissonconsulting/tinter)
* [haidawave](https://github.com/sebdalgarno/haidawave)

##### Selected (public) Shiny apps
* [Yield per Recruit tool](https://poissonconsulting.shinyapps.io/ypr-shiny/)
* [Kootenay Lake Trout Movement app](https://poissonconsulting.shinyapps.io/klexdatr-movement/)  
\  

### CERTIFICATIONS
* PADI Open Water Diver  
* Swiftwater Safety Rescue Technician Level 3  
* Occupational First Aid  
\  
\

`d3.js`, `leaflet.js`, `HTML`, `CSS`, `QGIS`, `ArcGIS`, `SQLite`, `Shiny`, `Machine Learning`, `Generalized Linear Model`, `R`, `Git`, `GitHub`, `Rstudio`, `ggplot2`, `tidyverse`


