---
title: ""
author: "Seb Dalgarno"
date: '2020-07-02'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
colorize <- function(x, color) {
  if (knitr::is_latex_output()) {
    sprintf("\\textcolor{%s}{%s}", color, x)
  } else if (knitr::is_html_output()) {
    sprintf("<span style='color: %s;'>%s</span>", color, 
      x)
  } else x
}

gg_color_hue <- function(n) {
  hues = seq(15, 375, length = n + 1)
  hcl(h = hues, l = 65, c = 100)[1:n]
}

library(RColorBrewer)

palette2 <- RColorBrewer::brewer.pal(2, "Dark2")
print(palette2)
palette5 <- RColorBrewer::brewer.pal(5, "Dark2")
print(palette5)
```

```{r work-experience-data, include=FALSE, echo=FALSE}
library(ggplot2)
library(plotly)
library(tibble)
library(dplyr)
library(lubridate)

pc.desc <- "Statistical modeling (Maximum Likelihood, Bayesian); R package development/maintenance; SQLite and Postgres database creation/management; Web app development; GIS."

se.desc <- "GIS; statistical modelling; data cleaning and SQLite database creation/management. Contracts with Parks Canada, Habitat Conservation Trust Foundation, Ministry of Forests, Lands and Natural Resource Operations, and Gowgaia Institute."

rg.desc <- "Species Distribution Modelling; shorebird and coastal/intertidal ecology; designed and conducted field work in remote Gwaii Haanas National Park Reserve over 3 weeks by kayak; predictive modelling/data management in R; results published in Avian Conservation Ecology journal."

ta.desc <- "Prepared and delivered presentations; supervised labs; graded assignments; topics covered by courses included statistical analysis, GIS and spatial analysis, remote sensing."

cws.desc <- "Lived and worked in remote part of K'uuna Gwaay Heritage Site/Conservancy retrieving ankle- band GPS loggers from breeding seabirds."

wcs.desc <- "Developed experimental design, coordinated field work and conducted statistical analyses to assess and predict above-ground biomass in tropical rainforest; results published in Pacific Conservation Biology journal."

uot.desc <- "Assisted Professor Neera Singh; conducted research on decentralized forest governance, community forestry, and carbon emission reduction projects from deforestation (REDD); prepared manuscripts for publication. "

df <- tibble(Employer = c("Poisson Consulting Ltd.",
                          "Self Employed",
                          "University of Guelph",
                          "University of Guelph",
                          "Canadian Wildlife Service",
                          "Wildlife Conservation Society",
                          "University of Toronto"),
             Role = c("Computational Biologist",
                      "Consultant",
                      "Researcher",
                      "Teaching Assistant",
                      "Researcher",
                      "Research Intern",
                      "Research Assistant"
                      ),
             Location = c("Haida Gwaii, BC",
                          "Haida Gwaii, BC",
                          "Guelph, ON",
                          "Guelph, ON",
                          "Haida Gwaii, BC",
                          "Manus, Papua New Guinea",
                          "Toronto, ON"
                          ),
             DateStart = c(ymd("2017-01-01"),
                           ymd("2016-09-01"),
                           ymd("2015-09-01"),
                           ymd("2014-09-01"),
                           ymd("2014-05-01"),
                           ymd("2012-09-01"),
                           ymd("2011-09-01")
                           ),
             DateEnd = c(Sys.Date(),
                         ymd("2016-12-31"),
                         ymd("2016-09-01"),
                         ymd("2016-09-01"),
                         ymd("2014-06-01"),
                         ymd("2014-09-01"),
                         ymd("2012-09-01")
                         ),
             Description = c(pc.desc,
                             se.desc,
                             rg.desc,
                             ta.desc,
                             cws.desc,
                             wcs.desc,
                             uot.desc
                             ))

df <- df %>% mutate(`Start Date` = format(DateStart, "%B %d, %Y"),
                    `End Date` = if_else(Employer == "Poisson Consulting Ltd.", "Ongoing", format(DateEnd, "%B %d, %Y"))) %>%
  arrange(desc(DateStart)) %>%
  mutate(row = as.factor(1:nrow(df)))

msc.desc <- "Predictive modeling of Black Oystercatcher distribution in Haida Gwaii, BC"
ba.desc <- "Interdisciplinary coursework on forestry and forest conservation, including core science requirements."

dfe <- tibble(University = c("University or Toronto",
                             "University of Guelph"),
              Degree = c("B.A. Forest Conservation",
                         "M.Sc. Geography"
                         ),
              Location = c("Toronto, ON",
                           "Guelph, ON"),
              DateStart = c(ymd("2006-09-01"),
                            ymd("2014-09-01")),
              DateEnd = c(ymd("2011-05-01"),
                          ymd("2016-09-01")),
              Description = c(ba.desc, msc.desc))

dfe <- dfe %>% mutate(`Start Date` = format(DateStart, "%B %d, %Y"),
                    `End Date` = format(DateEnd, "%B %d, %Y")) %>%
  arrange(desc(DateStart)) %>%
  mutate(row = as.factor(1:nrow(dfe)))
```
## Seb Dalgarno  
\

#### Masset, Haida Gwaii, BC  -  seb.dalgarno@gmail.com  -  250-626-8978 -  [GitHub Profile](https://github.com/sebdalgarno)  
\

I am a computational biologist with 6 years of R programming experience. My key skills include: R package development; Bayesian statistical modelling; web application development; SQLite and Postgres database management; SQL; GIS (top user of [sf StackOverflow tag](https://stackoverflow.com/tags/sf/topusers)). I have published work in scientific journals, co-authored numerous technical reports, and have experience managing and conducting remote ecological fieldwork.

<!-- * [StackOverflow](https://stackoverflow.com/users/7911031/sebdalgarno)   -->
\

### EDUCATION 
&nbsp;
```{r education-plot, echo=FALSE, fig.height=1}
# dfe <- dfe %>% arrange(DateStart)
gpe <- ggplot(data = dfe, aes(x = DateStart, xend = DateEnd, 
                            y = row, yend = row, color = row,
                            group = 1,
                    text = paste('University:', University, "<br>",
                                 'Degree:', Degree, "<br>",
                                 "Start Date:", `Start Date`, "<br>", 
                                 "End Date:", `End Date`))) + 
  geom_segment(size = 6, show.legend = FALSE) + 
  labs(x = NULL, y = NULL) +
  scale_color_manual(values = palette2) +
  theme_classic()  +
  theme(axis.text = element_text(size = 10),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        plot.title = element_text(size = 8)) +
  scale_x_date(limits = c(min(dfe$DateStart), max(df$DateEnd)))
# ggplotly(gpe, tooltip = c("text"), height = 150) %>% hide_legend() %>% config(displayModeBar = F)
gpe
```

##### `r colorize(dfe$Degree[1], palette2[1])`
###### `r dfe$University[1]` - `r dfe$Location[1]`
###### `r dfe[['Start Date']][1]` to `r dfe[['End Date']][1]`
`r dfe$Description[1]`

&nbsp;

##### `r colorize(dfe$Degree[2], palette2[2])`
###### `r dfe$University[2]` - `r dfe$Location[2]`
###### `r dfe[['Start Date']][2]` to `r dfe[['End Date']][2]`
`r dfe$Description[2]`

&nbsp;

### WORK EXPERIENCE 
&nbsp;

```{r work-experience-plot, echo=FALSE, fig.height=1.5}
library(plotly)
library(RColorBrewer)

# df <- df %>% arrange(DateStart)
gp <- ggplot(data = df[c(1, 2, 4, 6, 7),], aes(x = DateStart, xend = DateEnd, 
                            y = row, yend = row, color = row,
                            group = 1,
                    text = paste('Role:', Role, "<br>",
                                 'Employer:', Employer, "<br>",
                                 'Location:', Location, "<br>",
                                 "Start Date:", `Start Date`, "<br>", 
                                 "End Date:", `End Date`))) + 
  geom_segment(size = 6, show.legend = FALSE) + 
  labs(x = NULL, y = NULL) +
  scale_color_manual(values = palette5) +
  theme_classic() +
  # ggtitle("Hover over segment start/end to view more information.") +
  theme(axis.text = element_text(size = 10),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        plot.title = element_text(size = 8)) +
  scale_x_date(limits = c(min(df$DateStart), max(df$DateEnd)))
gp
# ggplotly(gp, tooltip = c("text"), height = 300) %>% hide_legend() %>% config(displayModeBar = F)
```

##### `r colorize(df$Role[1], palette5[1])`
###### [`r df$Employer[1]`](https://www.poissonconsulting.ca/) - `r df$Location[1]`
###### `r df[['Start Date']][1]` to `r df[['End Date']][1]`
`r df$Description[1]`

&nbsp;

##### `r colorize(df$Role[2], palette5[2])`
###### `r df$Employer[2]` - `r df$Location[2]`
###### `r df[['Start Date']][2]` to `r df[['End Date']][2]`
`r df$Description[2]`

&nbsp;

##### `r colorize(df$Role[4], palette5[3])`
###### `r df$Employer[4]` - `r df$Location[4]`
###### `r df[['Start Date']][4]` to `r df[['End Date']][4]`
`r df$Description[4]`

&nbsp;

##### `r colorize(df$Role[6], palette5[4])`
###### `r df$Employer[6]` - `r df$Location[6]`
###### `r df[['Start Date']][6]` to `r df[['End Date']][6]`
`r df$Description[6]`

&nbsp;

##### `r colorize(df$Role[7], palette5[5])`
###### `r df$Employer[7]` - `r df$Location[7]`
###### `r df[['Start Date']][7]` to `r df[['End Date']][7]`
`r df$Description[7]`

&nbsp;

### PUBLISHED WORK

##### Scientific Papers

* Dalgarno, S., J. E. Mersey, Z. Gedalof, and M. Lemon. 2017. Species-environment associations and predicted distribution of Black Oystercatcher breeding pairs in Haida Gwaii, British Columbia, Canada. Avian Conservation and Ecology 12(2):9. 
[link to paper](http://www.ace-eco.org/vol12/iss2/art9/)
* Arihafa, A., Dalgarno, S., and E. Neale. 2017.An estimate of above-ground carbon stock in tropical rainforest on Manus Island, Papua New Guinea. Pacific Conservation Biology 21(4) 307-314.
[link to paper](http://www.publish.csiro.au/PC/PC15015)

##### Selected Technical Reports
* [Quesnel Lake Exploitation Analysis](https://www.poissonconsulting.ca/analyses/quesnel-exploit-19/)
* [Trans Mountain Expansion Project Power Analysis](https://www.researchgate.net/publication/342184077_Trans_Mountain_Expansion_Project_and_Oil_Spills_Power_Analysis_on_Pacific_Salmon_Data)

##### Selected R packages
* [dbflobr](https://poissonconsulting.github.io/dbflobr/)
* [fwapgr](https://poissonconsulting.github.io/fwapgr/)

##### Selected web apps
* [bcgov ssdtools app](https://bcgov-env.shinyapps.io/ssdtools/)
* [Haida Gwaii logging history app](https://haidagwaiilogging.netlify.app/)  

### CERTIFICATIONS
* PADI Open Water Diver  
* Swiftwater Safety Rescue Technician Level 3  
* Occupational First Aid  
\  
\

`R`, `JavaScript`, `HTML`, `CSS`, `svelte`, `d3.js`, `SQLite`, `PostgreSQL`, `QGIS`, `Git`,  `ggplot2`, `tidyverse`, `Shiny`, `GitHub`, `Rstudio`


